---
title: "Curriculum Vitae"
format:
  html:
    toc: true
    toc-depth: 2
    toc-title: "Sections"
    css: cv-styles.css
---

```{r}
#| include: false

# Load required libraries
suppressPackageStartupMessages({
  library(yaml)
  library(scholar)
  library(dplyr)
  library(stringr)
  library(rvest)
  library(xml2)
  library(rentrez)
})

# Read CV data from YAML file
cv_data <- read_yaml("cv_data.yml")

# Helper function to format names with bold for Steven Hawken
bold_author <- function(text) {
  gsub("(Hawken S|Hawken, S|Steven Hawken|S Hawken|S\\.? Hawken)",
       "**\\1**",
       text,
       ignore.case = FALSE)
}

# Helper function to escape pipes in table cells
escape_pipes <- function(text) {
  if (is.null(text) || is.na(text)) return("")
  gsub("\\|", "/", text)
}
```

```{r}
#| output: asis
#| echo: false
#| warning: false
#| message: false

# Header with name and download button
personal <- cv_data$personal
name <- personal$name
positions <- personal$positions
links <- personal$links

cat("# ", name, "\n\n")

# Display positions
if (!is.null(positions) && length(positions) > 0) {
  for (pos in positions) {
    cat(pos, "\n\n")
  }
}

# Display links
if (!is.null(links)) {
  link_parts <- c()
  if (!is.null(links$ohri_profile)) link_parts <- c(link_parts, sprintf("[OHRI Profile](%s)", links$ohri_profile))
  if (!is.null(links$google_scholar)) link_parts <- c(link_parts, sprintf("[Google Scholar](%s)", links$google_scholar))
  if (!is.null(links$pubmed)) link_parts <- c(link_parts, sprintf("[PubMed](%s)", links$pubmed))
  if (!is.null(links$orcid) && links$orcid != "https://orcid.org/") link_parts <- c(link_parts, sprintf("[ORCID](%s)", links$orcid))
  if (!is.null(links$github)) link_parts <- c(link_parts, sprintf("[GitHub](%s)", links$github))
  if (length(link_parts) > 0) cat(paste(link_parts, collapse = " | "), "\n\n")
}

# Download PDF button
cat("<div style='margin: 20px 0;'>")
cat("<a href='shawken_CV.pdf' class='btn btn-primary' style='display: inline-block; padding: 10px 20px; background-color: #0066cc; color: white; text-decoration: none; border-radius: 4px;'>Download PDF</a>")
cat("</div>\n\n")
```

## Education

```{r}
#| output: asis
#| echo: false
#| warning: false
#| message: false

education <- cv_data$education

if (!is.null(education) && length(education) > 0) {
  for (edu in education) {
    cat("**", edu$degree, "** | ", edu$institution, " (", edu$year, ")\n\n")
  }
}
```

## Employment History

```{r}
#| output: asis
#| echo: false
#| warning: false
#| message: false

employment <- cv_data$employment

if (!is.null(employment) && length(employment) > 0) {
  for (emp in employment) {
    loc_part <- if (!is.null(emp$location) && emp$location != "") paste0(", ", emp$location) else ""
    cat("**", emp$years, "** | ", emp$title, ", ", emp$institution, loc_part, "\n\n")
  }
}
```

## Academic Honours and Awards

```{r}
#| output: asis
#| echo: false
#| warning: false
#| message: false

honours <- cv_data$academic_honours

if (!is.null(honours) && length(honours) > 0) {
  for (honour in honours) {
    cat("**", honour$year, "** — ", honour$award, ", ", honour$program, "\n\n")
  }
}
```

## Research Funding

### External Research Funding

```{r}
#| output: asis
#| echo: false
#| warning: false
#| message: false

external <- cv_data$external_research_funding

if (!is.null(external) && length(external) > 0) {
  # Create table data
  table_data <- data.frame(
    Years = character(),
    Source = character(),
    Title = character(),
    Role = character(),
    Amount = character(),
    stringsAsFactors = FALSE
  )

  for (grant in external) {
    # Format amount
    amount <- ""
    if (!is.null(grant$amount_cad)) {
      amount <- paste0("$", format(grant$amount_cad, big.mark = ","), " CAD")
    } else if (!is.null(grant$amount_usd)) {
      amount <- paste0("$", format(grant$amount_usd, big.mark = ","), " USD")
    } else if (!is.null(grant$amount_total_cad)) {
      amount <- paste0("$", format(grant$amount_total_cad, big.mark = ","), " CAD")
    }

    table_data <- rbind(table_data, data.frame(
      Years = if (!is.null(grant$year)) grant$year else "",
      Source = escape_pipes(grant$funder),
      Title = escape_pipes(grant$title),
      Role = escape_pipes(if (!is.null(grant$role)) grant$role else ""),
      Amount = amount,
      stringsAsFactors = FALSE
    ))
  }

  knitr::kable(table_data, format = "html")
}
```

### Internal Research Funding

```{r}
#| output: asis
#| echo: false
#| warning: false
#| message: false

internal <- cv_data$internal_research_funding

if (!is.null(internal) && length(internal) > 0) {
  # Create table data
  table_data <- data.frame(
    Years = character(),
    Source = character(),
    Title = character(),
    Role = character(),
    Amount = character(),
    stringsAsFactors = FALSE
  )

  for (grant in internal) {
    # Format amount
    amount <- ""
    if (!is.null(grant$amount_cad)) {
      amount <- paste0("$", format(grant$amount_cad, big.mark = ","), " CAD")
    }

    table_data <- rbind(table_data, data.frame(
      Years = if (!is.null(grant$year)) grant$year else "",
      Source = escape_pipes(grant$funder),
      Title = escape_pipes(grant$title),
      Role = escape_pipes(if (!is.null(grant$role)) grant$role else ""),
      Amount = amount,
      stringsAsFactors = FALSE
    ))
  }

  knitr::kable(table_data, format = "html")
}
```

## Teaching

### Graduate Courses

```{r}
#| output: asis
#| echo: false
#| warning: false
#| message: false

teaching <- cv_data$teaching

if (!is.null(teaching$graduate_courses) && length(teaching$graduate_courses) > 0) {
  for (course in teaching$graduate_courses) {
    cat("**", course$year, "** | ", course$code, ": ", course$title, "\n\n")
    cat(course$institution, "\n\n")
    if (!is.null(course$description)) {
      cat(course$description, "\n\n")
    }
  }
} else {
  cat("*No graduate courses listed*\n\n")
}
```

### Guest Lectures

```{r}
#| output: asis
#| echo: false
#| warning: false
#| message: false

if (!is.null(teaching$guest_lectures) && length(teaching$guest_lectures) > 0) {
  for (lecture in teaching$guest_lectures) {
    cat("**", lecture$year, "** | ", lecture$title, "\n\n")
    cat(lecture$course, ", ", lecture$institution, "\n\n")
  }
} else {
  cat("*No guest lectures listed*\n\n")
}
```

## Conference Session Organizing

```{r}
#| output: asis
#| echo: false
#| warning: false
#| message: false

conf_sessions <- cv_data$conference_session_organizing

if (!is.null(conf_sessions) && length(conf_sessions) > 0) {
  for (session in conf_sessions) {
    cat("**", session$year, "** — ", session$title, "\n\n")
    cat(session$role, ", ", session$conference, ", ", session$location, "\n\n")
  }
} else {
  cat("*No conference sessions listed*\n\n")
}
```

## Trainee Supervision

### Current / In Progress

```{r}
#| output: asis
#| echo: false
#| warning: false
#| message: false

trainee <- cv_data$trainee_supervision

if (!is.null(trainee$current_inprogress) && length(trainee$current_inprogress) > 0) {
  for (student in trainee$current_inprogress) {
    cat("**", student$name, "**\n\n")
    cat(student$degree, " | ", student$institution, " (", student$years, ")\n\n")
    cat("Thesis: ", student$thesis_topic, "\n\n")
    cat("Role: ", student$role, "\n\n")
  }
} else {
  cat("*No students currently supervised*\n\n")
}
```

### Completed

```{r}
#| output: asis
#| echo: false
#| warning: false
#| message: false

if (!is.null(trainee$completed) && length(trainee$completed) > 0) {
  for (student in trainee$completed) {
    cat("**", student$name, "**\n\n")
    cat(student$degree, " | ", student$institution, " (", student$years, ")\n\n")
    cat("Thesis: ", student$thesis_topic, "\n\n")
    cat("Role: ", student$role, "\n\n")
    if (!is.null(student$current_position)) {
      cat("Current Position: ", student$current_position, "\n\n")
    }
    if (!is.null(student$award)) {
      cat("Award: ", student$award, "\n\n")
    }
  }
} else {
  cat("*No completed students listed*\n\n")
}
```

## Thesis Advisory Committee Memberships

### In Progress

```{r}
#| output: asis
#| echo: false
#| warning: false
#| message: false

tac <- cv_data$thesis_advisory_committee_member
if (!is.null(tac$in_progress) &&
    length(tac$in_progress) > 0) {
  for (member in tac$in_progress) {
    cat("- ", member$name, " (", member$degree, ")\n")
  }
  cat("\n")
} else {
  cat("*No current memberships*\n\n")
}
```

### Completed

```{r}
#| output: asis
#| echo: false
#| warning: false
#| message: false

tac <- cv_data$thesis_advisory_committee_member
if (!is.null(tac$completed) &&
    length(tac$completed) > 0) {
  for (member in tac$completed) {
    cat("- ", member$name, " (", member$degree, ", ", member$year, ")\n")
  }
  cat("\n")
} else {
  cat("*No completed memberships listed*\n\n")
}
```

## Scholarly Activities

### Thesis Examiner

```{r}
#| output: asis
#| echo: false
#| warning: false
#| message: false

examiner <- cv_data$thesis_examiner

if (!is.null(examiner) && length(examiner) > 0) {
  for (exam in examiner) {
    cat("**", exam$date, "** — ", exam$candidate, ", ", exam$degree, ", ", exam$institution, "\n\n")
  }
}
```

### Thesis Defense Chair

```{r}
#| output: asis
#| echo: false
#| warning: false
#| message: false

chair <- cv_data$thesis_defense_chairperson

if (!is.null(chair) && length(chair) > 0) {
  for (c in chair) {
    cat("**", c$date, "** — ", c$candidate, ", ", c$degree, "\n\n")
  }
}
```

### Thesis Proposal Examiner

```{r}
#| output: asis
#| echo: false
#| warning: false
#| message: false

prop_examiner <- cv_data$thesis_proposal_examiner

if (!is.null(prop_examiner) && length(prop_examiner) > 0) {
  for (prop in prop_examiner) {
    cat("**", prop$date, "** — ", prop$candidate, ", ", prop$degree, "\n\n")
  }
}
```

### PhD Comprehensive Examiner

```{r}
#| output: asis
#| echo: false
#| warning: false
#| message: false

comp_examiner <- cv_data$phd_comprehensive_examiner

if (!is.null(comp_examiner) && length(comp_examiner) > 0) {
  for (comp in comp_examiner) {
    cat("**", comp$date, "** — ", comp$candidate, ", ", comp$degree)
    if (!is.null(comp$note)) {
      cat(" (", comp$note, ")")
    }
    cat("\n\n")
  }
}
```

## Data Safety Monitoring Committees

```{r}
#| output: asis
#| echo: false
#| warning: false
#| message: false

dsmc <- cv_data$data_safety_monitoring_committees

if (!is.null(dsmc) && length(dsmc) > 0) {
  for (committee in dsmc) {
    cat("**", committee$years, "** — Member, DSMC\n\n")
    cat("Study: ", committee$study, "\n\n")
    cat("PI: ", committee$pi, ", ", committee$institution, "\n\n")
  }
} else {
  cat("*No DSMC memberships listed*\n\n")
}
```

## Grant Review Committees

```{r}
#| output: asis
#| echo: false
#| warning: false
#| message: false

grant_review <- cv_data$grant_review_committees

if (!is.null(grant_review) && length(grant_review) > 0) {
  for (committee in grant_review) {
    cat("**", committee$date, "** — Peer Reviewer, ", committee$funder, ", ", committee$program)
    if (!is.null(committee$effort)) {
      cat("\n\n", committee$effort)
    }
    cat("\n\n")
  }
} else {
  cat("*No grant review committee memberships listed*\n\n")
}
```

## Editorial and Peer Review

```{r}
#| output: asis
#| echo: false
#| warning: false
#| message: false

editorial <- cv_data$editorial_review

if (!is.null(editorial$journals) && length(editorial$journals) > 0) {
  cat("**Journal Editorial Boards and Peer Review**\n\n")
  for (journal in editorial$journals) {
    cat("- ", journal, "\n")
  }
  cat("\n")
}
```

## Invited Talks and Seminars

```{r}
#| output: asis
#| echo: false
#| warning: false
#| message: false

invited <- cv_data$invited_talks_seminars

if (!is.null(invited) && length(invited) > 0) {
  for (talk in invited) {
    cat("**", talk$year, "** — ", talk$title, " | ", talk$event)
    if (!is.null(talk$location)) {
      cat(" (", talk$location, ")")
    }
    cat("\n\n")
  }
} else {
  cat("*No invited talks listed*\n\n")
}
```

## Publications

```{r}
#| output: false
#| echo: false
#| warning: false
#| message: true
#| cache: false
#| freeze: false

# Sentinel: prove this chunk ran (even if Quarto suppresses messages)
cat("---- pub fetch chunk started ", format(Sys.time()), " ----\n",
    file = "_pubmed_fetch.log", append = TRUE)

# ---- Google Scholar profile (for stats only: h-index, i10, total cites) ----
profile <- NULL
tryCatch({
  profile <- scholar::get_profile("aTyysxgAAAAJ")
}, error = function(e) {
  profile <- NULL
})

# ---- Peer-reviewed publications: MyNCBI scrape -> rentrez -> RDS cache ----
pubmed_cache_file <- "_pubmed_cache.rds"
myncbi_url <- cv_data$personal$links$pubmed

# Normalised columns for downstream display:
#   authors, title, journal, date, pmid
empty_pubs <- data.frame(
  authors = character(), title = character(), journal = character(),
  date = character(), pmid = character(), stringsAsFactors = FALSE
)

# --- Method 1: scrape MyNCBI public bibliography ---
# Each citation is a <div class="citation"> containing:
#   .authors, <a href="/pubmed/PMID/">title</a>, .source (journal),
#   .pubdate, .volume, .issue, .doi, .pmid, plus
#   <input class="citation-check" pmid="..."> with the PMID as an attribute.
# MyNCBI paginates at 50 citations/page; ?pageSize= is ignored — we walk
# ?page=1,2,3... until a page returns 0 citations or repeats PMIDs.
fetch_myncbi <- function(url, max_pages = 20) {
  safe_text <- function(node) {
    if (inherits(node, "xml_missing")) return("")
    txt <- rvest::html_text2(node)
    if (is.null(txt) || is.na(txt)) "" else txt
  }

  parse_page <- function(page) {
    items <- page %>% rvest::html_elements("div.citation")
    if (length(items) == 0) return(NULL)

    rows <- lapply(items, function(item) {
      docsum <- rvest::html_element(item, "div.ncbi-docsum")
      if (inherits(docsum, "xml_missing")) docsum <- item

      authors <- safe_text(rvest::html_element(docsum, ".authors"))
      authors <- sub("\\.\\s*$", "", trimws(authors))

      title_node <- rvest::html_element(docsum, "a[href*='/pubmed/']")
      title <- trimws(safe_text(title_node))

      journal <- trimws(safe_text(rvest::html_element(docsum, ".source")))
      pubdate <- sub(";\\s*$", "", trimws(safe_text(
        rvest::html_element(docsum, ".pubdate"))))
      volume  <- trimws(safe_text(rvest::html_element(docsum, ".volume")))
      issue   <- trimws(safe_text(rvest::html_element(docsum, ".issue")))

      date <- pubdate
      if (nzchar(volume)) date <- paste0(date, ";", volume)
      if (nzchar(issue))  date <- paste0(date, issue)
      date <- trimws(date)

      pmid <- ""
      check <- rvest::html_element(item, "input.citation-check")
      if (!inherits(check, "xml_missing")) {
        attr_val <- rvest::html_attr(check, "pmid")
        if (!is.null(attr_val) && !is.na(attr_val)) pmid <- attr_val
      }
      if (!nzchar(pmid)) {
        ptxt <- safe_text(rvest::html_element(docsum, ".pmid"))
        m <- regmatches(ptxt, regexpr("\\d+", ptxt))
        if (length(m)) pmid <- m
      }
      if (!nzchar(pmid) && !inherits(title_node, "xml_missing")) {
        href <- rvest::html_attr(title_node, "href")
        if (!is.null(href) && !is.na(href)) {
          m <- regmatches(href, regexpr("\\d+", href))
          if (length(m)) pmid <- m
        }
      }

      data.frame(authors = authors, title = title, journal = journal,
                 date = date, pmid = pmid, stringsAsFactors = FALSE)
    })
    do.call(rbind, rows)
  }

  tryCatch({
    # MyNCBI's pagination uses bare ?page=N and ignores it when appended to
    # an existing query string (e.g. ?sort=date&direction=descending&page=2
    # silently returns page 1). Strip the existing query before paging.
    base_url <- sub("\\?.*$", "", url)
    acc <- list()
    seen_pmids <- character(0)

    log_path <- "_pubmed_fetch.log"
    log_msg <- function(...) {
      cat(format(Sys.time()), " ", ..., "\n",
          sep = "", file = log_path, append = TRUE)
    }
    cat("---- new fetch ", format(Sys.time()), " ----\n",
        file = log_path, append = TRUE)
    log_msg("base_url = ", base_url)

    for (p in seq_len(max_pages)) {
      page_url <- paste0(base_url, "?page=", p)
      log_msg("fetching: ", page_url)
      page <- tryCatch(rvest::read_html(page_url),
                       error = function(e) {
                         log_msg("  read_html error: ", conditionMessage(e))
                         NULL
                       })
      if (is.null(page)) break

      df   <- parse_page(page)
      n_raw <- if (is.null(df)) 0L else nrow(df)
      log_msg("  parsed ", n_raw, " citations from page ", p)
      if (is.null(df) || nrow(df) == 0) break

      new_rows <- df[!df$pmid %in% seen_pmids, , drop = FALSE]
      log_msg("  ", nrow(new_rows), " new (not duplicates)")
      if (nrow(new_rows) == 0) break

      acc[[length(acc) + 1]] <- new_rows
      seen_pmids <- c(seen_pmids, new_rows$pmid)

      if (nrow(df) < 50) {
        log_msg("  partial page (<50), stopping")
        break
      }
    }
    log_msg("MyNCBI total collected: ", length(seen_pmids))

    if (length(acc) == 0) return(NULL)
    df <- do.call(rbind, acc)
    df <- df[nchar(df$title) > 0 & nchar(df$pmid) > 0, , drop = FALSE]
    if (nrow(df) == 0) return(NULL)
    df
  }, error = function(e) {
    message("MyNCBI scrape failed: ", conditionMessage(e))
    NULL
  })
}

# --- Method 2: rentrez PubMed search ---
# Now the PRIMARY source: MyNCBI uses JS-based pagination so a non-headless
# scraper can't get past page 1.
# Query strategy: match on ORCID (cleanest) OR on author name + Ottawa-area
# affiliations (catches pre-ORCID-adoption papers, ~pre-2015).
fetch_rentrez <- function(orcid = "0000-0002-3341-9022",
                          author_term = "Hawken S[Author]",
                          aff_terms = c("Ottawa", "OHRI",
                                        "Institute for Clinical Evaluative Sciences",
                                        "ICES",
                                        "CHEO",
                                        "Children's Hospital of Eastern Ontario"),
                          retmax = 1000) {
  tryCatch({
    aff <- paste0("(",
                  paste(sprintf("%s[Affiliation]", aff_terms), collapse = " OR "),
                  ")")
    aff_clause <- paste0("(", author_term, " AND ", aff, ")")

    if (!is.null(orcid) && nzchar(orcid)) {
      query <- paste0("(", orcid, "[AUID] OR ", aff_clause, ")")
    } else {
      query <- aff_clause
    }

    sres <- rentrez::entrez_search(db = "pubmed", term = query, retmax = retmax)
    if (length(sres$ids) == 0) return(NULL)

    # Fetch in batches of 100 to be polite.
    # NB: parsed = TRUE would return an XMLInternalDocument from the old {XML}
    # package, which xml2's functions don't recognise. Fetch as text and
    # reparse with xml2 so the rest of the code can use xml_find_*.
    id_chunks <- split(sres$ids, ceiling(seq_along(sres$ids) / 100))
    xml_docs <- lapply(id_chunks, function(ids) {
      raw <- rentrez::entrez_fetch(db = "pubmed", id = ids,
                                   rettype = "xml", parsed = FALSE)
      xml2::read_xml(raw)
    })

    parse_article <- function(art) {
      gx <- function(xp) {
        n <- xml2::xml_find_first(art, xp)
        if (inherits(n, "xml_missing")) "" else xml2::xml_text(n)
      }
      pmid    <- gx(".//PMID")
      title   <- gx(".//ArticleTitle")
      journal <- gx(".//Journal/Title")
      year    <- gx(".//JournalIssue/PubDate/Year")
      if (!nzchar(year)) {
        md <- gx(".//JournalIssue/PubDate/MedlineDate")
        year <- substr(md, 1, 4)
      }
      volume <- gx(".//JournalIssue/Volume")
      issue  <- gx(".//JournalIssue/Issue")
      pages  <- gx(".//Pagination/MedlinePgn")

      authors_nodes <- xml2::xml_find_all(art, ".//AuthorList/Author")
      authors <- vapply(authors_nodes, function(a) {
        last <- xml2::xml_text(xml2::xml_find_first(a, "LastName"))
        init <- xml2::xml_text(xml2::xml_find_first(a, "Initials"))
        if (is.na(last)) {
          coll <- xml2::xml_text(xml2::xml_find_first(a, "CollectiveName"))
          if (is.na(coll)) "" else coll
        } else {
          paste0(last, if (!is.na(init) && nzchar(init)) paste0(" ", init))
        }
      }, character(1))
      authors <- paste(authors[nzchar(authors)], collapse = ", ")

      date <- year
      vip <- ""
      if (nzchar(volume)) vip <- volume
      if (nzchar(issue))  vip <- paste0(vip, "(", issue, ")")
      if (nzchar(pages))  vip <- paste0(vip, ":", pages)
      if (nzchar(vip))    date <- paste0(date, ";", vip)

      data.frame(
        authors = authors, title = title, journal = journal,
        date = date, pmid = pmid,
        year = suppressWarnings(as.integer(substr(year, 1, 4))),
        stringsAsFactors = FALSE
      )
    }

    all_rows <- list()
    for (doc in xml_docs) {
      arts <- xml2::xml_find_all(doc, ".//PubmedArticle")
      for (a in arts) all_rows[[length(all_rows) + 1]] <- parse_article(a)
    }
    df <- do.call(rbind, all_rows)
    if (is.null(df) || nrow(df) == 0) return(NULL)

    # Most recent first
    df <- df[order(-df$year, df$title), ]
    df$year <- NULL
    df
  }, error = function(e) {
    message("rentrez fetch failed: ", conditionMessage(e))
    NULL
  })
}

# --- Execute with fallback chain ---
# rentrez is primary (MyNCBI scraping is broken — see fetch_myncbi comment).
# fetch_myncbi is kept defined in case NCBI ever returns to server-side paging.
pubmed_pubs <- fetch_rentrez()
pubmed_source <- if (!is.null(pubmed_pubs)) "PubMed (rentrez)" else NA_character_

if (is.null(pubmed_pubs)) {
  pubmed_pubs <- fetch_myncbi(myncbi_url)
  if (!is.null(pubmed_pubs)) pubmed_source <- "MyNCBI"
}

if (!is.null(pubmed_pubs) && nrow(pubmed_pubs) > 0) {
  saveRDS(pubmed_pubs, pubmed_cache_file)
} else if (file.exists(pubmed_cache_file)) {
  pubmed_pubs <- readRDS(pubmed_cache_file)
  pubmed_source <- "cached"
}

if (is.null(pubmed_pubs)) pubmed_pubs <- empty_pubs
```

```{r}
#| output: asis
#| echo: false
#| warning: false
#| message: false

# Display profile statistics from Google Scholar if available
if (!is.null(profile)) {
  cat("**Profile Statistics (Google Scholar):**\n\n")
  cat("- **H-Index**: ", profile$h_index, "\n")
  cat("- **i10-Index**: ", profile$i10_index, "\n")
  cat("- **Total Citations**: ", profile$total_cites, "\n\n")
}

cat("### Peer-Reviewed Publications\n\n")

# Display publications from PubMed, numbered 1..N (no year grouping)
if (!is.null(pubmed_pubs) && nrow(pubmed_pubs) > 0) {
  cat("*Source: ", pubmed_source, " — ", nrow(pubmed_pubs),
      " publication(s).*\n\n", sep = "")

  for (i in seq_len(nrow(pubmed_pubs))) {
    pub <- pubmed_pubs[i, ]

    authors <- bold_author(pub$authors)
    title   <- pub$title
    journal <- pub$journal
    date    <- pub$date
    pmid    <- pub$pmid

    # Build Vancouver-ish citation: Authors. Title. *Journal*. Date. [PMID: #####]
    citation <- paste0(i, ". ", authors, ". ")

    if (!is.null(title) && !is.na(title) && nzchar(title)) {
      # Strip trailing period from title if present, then add our own.
      title_clean <- sub("\\.\\s*$", "", title)
      citation <- paste0(citation, "**", title_clean, "**. ")
    }

    if (!is.null(journal) && !is.na(journal) && nzchar(journal)) {
      citation <- paste0(citation, "*", journal, "*. ")
    }

    if (!is.null(date) && !is.na(date) && nzchar(date)) {
      date_clean <- sub("\\.\\s*$", "", date)
      citation <- paste0(citation, date_clean, ". ")
    }

    if (!is.null(pmid) && !is.na(pmid) && nzchar(pmid)) {
      citation <- paste0(
        citation,
        sprintf("[PMID: [%s](https://pubmed.ncbi.nlm.nih.gov/%s/)]", pmid, pmid)
      )
    }

    cat(citation, "\n\n")
  }
} else {
  cat("*Publications not currently available. Please check again later.*\n\n")
}
```

### Preprints

```{r}
#| output: asis
#| echo: false
#| warning: false
#| message: false

preprints <- cv_data$preprints

if (!is.null(preprints) && length(preprints) > 0) {
  for (preprint in preprints) {
    authors <- bold_author(preprint$authors)
    cat("**", preprint$title, "**\n\n")
    cat(authors, ". ")
    if (!is.null(preprint$date)) {
      cat(preprint$date, ". ")
    }
    cat(preprint$arxiv, "\n\n")
  }
} else {
  cat("*No preprints listed*\n\n")
}
```

---

```{r}
#| output: asis
#| echo: false
#| warning: false
#| message: false

# Footer with last updated date
update_date <- Sys.Date()
cat("**Last updated:** ", format(update_date, "%B %d, %Y"), "\n\n")
```
