---
title: "Curriculum Vitae"
format:
  html:
    toc: true
    toc-depth: 2
    toc-title: "Sections"
    css: cv-styles.css
---

```{r}
#| include: false

# Load required libraries
suppressPackageStartupMessages({
  library(yaml)
  library(scholar)
  library(dplyr)
  library(stringr)
})

# Read CV data from YAML file
cv_data <- read_yaml("cv_data.yml")

# Helper function to format names with bold for Steven Hawken
bold_author <- function(text) {
  gsub("(Hawken S|Hawken, S|Steven Hawken|S Hawken|S\\.? Hawken)",
       "**\\1**",
       text,
       ignore.case = FALSE)
}

# Helper function to escape pipes in table cells
escape_pipes <- function(text) {
  if (is.null(text) || is.na(text)) return("")
  gsub("\\|", "/", text)
}
```

```{r}
#| output: asis
#| echo: false
#| warning: false
#| message: false

# Header with name and download button
personal <- cv_data$personal
name <- personal$name
positions <- personal$positions
links <- personal$links

cat("# ", name, "\n\n")

# Display positions
if (!is.null(positions) && length(positions) > 0) {
  for (pos in positions) {
    cat(pos, "\n\n")
  }
}

# Display links
if (!is.null(links)) {
  link_parts <- c()
  if (!is.null(links$ohri_profile)) link_parts <- c(link_parts, sprintf("[OHRI Profile](%s)", links$ohri_profile))
  if (!is.null(links$google_scholar)) link_parts <- c(link_parts, sprintf("[Google Scholar](%s)", links$google_scholar))
  if (!is.null(links$pubmed)) link_parts <- c(link_parts, sprintf("[PubMed](%s)", links$pubmed))
  if (!is.null(links$orcid) && links$orcid != "https://orcid.org/") link_parts <- c(link_parts, sprintf("[ORCID](%s)", links$orcid))
  if (!is.null(links$github)) link_parts <- c(link_parts, sprintf("[GitHub](%s)", links$github))
  if (length(link_parts) > 0) cat(paste(link_parts, collapse = " | "), "\n\n")
}

# Download PDF button
cat("<div style='margin: 20px 0;'>")
cat("<a href='shawken_CV.pdf' class='btn btn-primary' style='display: inline-block; padding: 10px 20px; background-color: #0066cc; color: white; text-decoration: none; border-radius: 4px;'>Download PDF</a>")
cat("</div>\n\n")
```

## Education

```{r}
#| output: asis
#| echo: false
#| warning: false
#| message: false

education <- cv_data$education

if (!is.null(education) && length(education) > 0) {
  for (edu in education) {
    cat("**", edu$degree, "** | ", edu$institution, " (", edu$year, ")\n\n")
  }
}
```

## Employment History

```{r}
#| output: asis
#| echo: false
#| warning: false
#| message: false

employment <- cv_data$employment

if (!is.null(employment) && length(employment) > 0) {
  for (emp in employment) {
    loc_part <- if (!is.null(emp$location) && emp$location != "") paste0(", ", emp$location) else ""
    cat("**", emp$years, "** | ", emp$title, ", ", emp$institution, loc_part, "\n\n")
  }
}
```

## Academic Honours and Awards

```{r}
#| output: asis
#| echo: false
#| warning: false
#| message: false

honours <- cv_data$academic_honours

if (!is.null(honours) && length(honours) > 0) {
  for (honour in honours) {
    cat("**", honour$year, "** — ", honour$award, ", ", honour$program, "\n\n")
  }
}
```

## Research Funding

### External Research Funding

```{r}
#| output: asis
#| echo: false
#| warning: false
#| message: false

external <- cv_data$external_research_funding

if (!is.null(external) && length(external) > 0) {
  # Create table data
  table_data <- data.frame(
    Years = character(),
    Source = character(),
    Title = character(),
    Role = character(),
    Amount = character(),
    stringsAsFactors = FALSE
  )

  for (grant in external) {
    # Format amount
    amount <- ""
    if (!is.null(grant$amount_cad)) {
      amount <- paste0("$", format(grant$amount_cad, big.mark = ","), " CAD")
    } else if (!is.null(grant$amount_usd)) {
      amount <- paste0("$", format(grant$amount_usd, big.mark = ","), " USD")
    } else if (!is.null(grant$amount_total_cad)) {
      amount <- paste0("$", format(grant$amount_total_cad, big.mark = ","), " CAD")
    }

    table_data <- rbind(table_data, data.frame(
      Years = if (!is.null(grant$year)) grant$year else "",
      Source = escape_pipes(grant$funder),
      Title = escape_pipes(grant$title),
      Role = escape_pipes(if (!is.null(grant$role)) grant$role else ""),
      Amount = amount,
      stringsAsFactors = FALSE
    ))
  }

  knitr::kable(table_data, format = "html")
}
```

### Internal Research Funding

```{r}
#| output: asis
#| echo: false
#| warning: false
#| message: false

internal <- cv_data$internal_research_funding

if (!is.null(internal) && length(internal) > 0) {
  # Create table data
  table_data <- data.frame(
    Years = character(),
    Source = character(),
    Title = character(),
    Role = character(),
    Amount = character(),
    stringsAsFactors = FALSE
  )

  for (grant in internal) {
    # Format amount
    amount <- ""
    if (!is.null(grant$amount_cad)) {
      amount <- paste0("$", format(grant$amount_cad, big.mark = ","), " CAD")
    }

    table_data <- rbind(table_data, data.frame(
      Years = if (!is.null(grant$year)) grant$year else "",
      Source = escape_pipes(grant$funder),
      Title = escape_pipes(grant$title),
      Role = escape_pipes(if (!is.null(grant$role)) grant$role else ""),
      Amount = amount,
      stringsAsFactors = FALSE
    ))
  }

  knitr::kable(table_data, format = "html")
}
```

## Teaching

### Graduate Courses

```{r}
#| output: asis
#| echo: false
#| warning: false
#| message: false

teaching <- cv_data$teaching

if (!is.null(teaching$graduate_courses) && length(teaching$graduate_courses) > 0) {
  for (course in teaching$graduate_courses) {
    cat("**", course$year, "** | ", course$code, ": ", course$title, "\n\n")
    cat(course$institution, "\n\n")
    if (!is.null(course$description)) {
      cat(course$description, "\n\n")
    }
  }
} else {
  cat("*No graduate courses listed*\n\n")
}
```

### Guest Lectures

```{r}
#| output: asis
#| echo: false
#| warning: false
#| message: false

if (!is.null(teaching$guest_lectures) && length(teaching$guest_lectures) > 0) {
  for (lecture in teaching$guest_lectures) {
    cat("**", lecture$year, "** | ", lecture$title, "\n\n")
    cat(lecture$course, ", ", lecture$institution, "\n\n")
  }
} else {
  cat("*No guest lectures listed*\n\n")
}
```

## Conference Session Organizing

```{r}
#| output: asis
#| echo: false
#| warning: false
#| message: false

conf_sessions <- cv_data$conference_session_organizing

if (!is.null(conf_sessions) && length(conf_sessions) > 0) {
  for (session in conf_sessions) {
    cat("**", session$year, "** — ", session$title, "\n\n")
    cat(session$role, ", ", session$conference, ", ", session$location, "\n\n")
  }
} else {
  cat("*No conference sessions listed*\n\n")
}
```

## Trainee Supervision

### Current / In Progress

```{r}
#| output: asis
#| echo: false
#| warning: false
#| message: false

trainee <- cv_data$trainee_supervision

if (!is.null(trainee$current_inprogress) && length(trainee$current_inprogress) > 0) {
  for (student in trainee$current_inprogress) {
    cat("**", student$name, "**\n\n")
    cat(student$degree, " | ", student$institution, " (", student$years, ")\n\n")
    cat("Thesis: ", student$thesis_topic, "\n\n")
    cat("Role: ", student$role, "\n\n")
  }
} else {
  cat("*No students currently supervised*\n\n")
}
```

### Completed

```{r}
#| output: asis
#| echo: false
#| warning: false
#| message: false

if (!is.null(trainee$completed) && length(trainee$completed) > 0) {
  for (student in trainee$completed) {
    cat("**", student$name, "**\n\n")
    cat(student$degree, " | ", student$institution, " (", student$years, ")\n\n")
    cat("Thesis: ", student$thesis_topic, "\n\n")
    cat("Role: ", student$role, "\n\n")
    if (!is.null(student$current_position)) {
      cat("Current Position: ", student$current_position, "\n\n")
    }
    if (!is.null(student$award)) {
      cat("Award: ", student$award, "\n\n")
    }
  }
} else {
  cat("*No completed students listed*\n\n")
}
```

## Thesis Advisory Committee Memberships

### In Progress

```{r}
#| output: asis
#| echo: false
#| warning: false
#| message: false

tac <- cv_data$thesis_advisory_committee_member
if (!is.null(tac$in_progress) &&
    length(tac$in_progress) > 0) {
  for (member in tac$in_progress) {
    cat("- ", member$name, " (", member$degree, ")\n")
  }
  cat("\n")
} else {
  cat("*No current memberships*\n\n")
}
```

### Completed

```{r}
#| output: asis
#| echo: false
#| warning: false
#| message: false

tac <- cv_data$thesis_advisory_committee_member
if (!is.null(tac$completed) &&
    length(tac$completed) > 0) {
  for (member in tac$completed) {
    cat("- ", member$name, " (", member$degree, ", ", member$year, ")\n")
  }
  cat("\n")
} else {
  cat("*No completed memberships listed*\n\n")
}
```

## Scholarly Activities

### Thesis Examiner

```{r}
#| output: asis
#| echo: false
#| warning: false
#| message: false

examiner <- cv_data$thesis_examiner

if (!is.null(examiner) && length(examiner) > 0) {
  for (exam in examiner) {
    cat("**", exam$date, "** — ", exam$candidate, ", ", exam$degree, ", ", exam$institution, "\n\n")
  }
}
```

### Thesis Defense Chair

```{r}
#| output: asis
#| echo: false
#| warning: false
#| message: false

chair <- cv_data$thesis_defense_chairperson

if (!is.null(chair) && length(chair) > 0) {
  for (c in chair) {
    cat("**", c$date, "** — ", c$candidate, ", ", c$degree, "\n\n")
  }
}
```

### Thesis Proposal Examiner

```{r}
#| output: asis
#| echo: false
#| warning: false
#| message: false

prop_examiner <- cv_data$thesis_proposal_examiner

if (!is.null(prop_examiner) && length(prop_examiner) > 0) {
  for (prop in prop_examiner) {
    cat("**", prop$date, "** — ", prop$candidate, ", ", prop$degree, "\n\n")
  }
}
```

### PhD Comprehensive Examiner

```{r}
#| output: asis
#| echo: false
#| warning: false
#| message: false

comp_examiner <- cv_data$phd_comprehensive_examiner

if (!is.null(comp_examiner) && length(comp_examiner) > 0) {
  for (comp in comp_examiner) {
    cat("**", comp$date, "** — ", comp$candidate, ", ", comp$degree)
    if (!is.null(comp$note)) {
      cat(" (", comp$note, ")")
    }
    cat("\n\n")
  }
}
```

## Data Safety Monitoring Committees

```{r}
#| output: asis
#| echo: false
#| warning: false
#| message: false

dsmc <- cv_data$data_safety_monitoring_committees

if (!is.null(dsmc) && length(dsmc) > 0) {
  for (committee in dsmc) {
    cat("**", committee$years, "** — Member, DSMC\n\n")
    cat("Study: ", committee$study, "\n\n")
    cat("PI: ", committee$pi, ", ", committee$institution, "\n\n")
  }
} else {
  cat("*No DSMC memberships listed*\n\n")
}
```

## Grant Review Committees

```{r}
#| output: asis
#| echo: false
#| warning: false
#| message: false

grant_review <- cv_data$grant_review_committees

if (!is.null(grant_review) && length(grant_review) > 0) {
  for (committee in grant_review) {
    cat("**", committee$date, "** — Peer Reviewer, ", committee$funder, ", ", committee$program)
    if (!is.null(committee$effort)) {
      cat("\n\n", committee$effort)
    }
    cat("\n\n")
  }
} else {
  cat("*No grant review committee memberships listed*\n\n")
}
```

## Editorial and Peer Review

```{r}
#| output: asis
#| echo: false
#| warning: false
#| message: false

editorial <- cv_data$editorial_review

if (!is.null(editorial$journals) && length(editorial$journals) > 0) {
  cat("**Journal Editorial Boards and Peer Review**\n\n")
  for (journal in editorial$journals) {
    cat("- ", journal, "\n")
  }
  cat("\n")
}
```

## Invited Talks and Seminars

```{r}
#| output: asis
#| echo: false
#| warning: false
#| message: false

invited <- cv_data$invited_talks_seminars

if (!is.null(invited) && length(invited) > 0) {
  for (talk in invited) {
    cat("**", talk$year, "** — ", talk$title, " | ", talk$event)
    if (!is.null(talk$location)) {
      cat(" (", talk$location, ")")
    }
    cat("\n\n")
  }
} else {
  cat("*No invited talks listed*\n\n")
}
```

## Publications

```{r}
#| output: false
#| echo: false
#| warning: false
#| message: false

# Try to get publications from Google Scholar with caching
cache_file <- "_pub_cache.rds"
pubs <- NULL
profile <- NULL

tryCatch({
  # Attempt to fetch from Google Scholar
  pubs <- scholar::get_publications("aTyysxgAAAAJ")
  if (!is.null(pubs) && nrow(pubs) > 0) {
    pubs <- pubs[order(-pubs$year, pubs$title), ]
    saveRDS(pubs, cache_file)
  }
}, error = function(e) {
  # Fall back to cache if available
  if (file.exists(cache_file)) {
    pubs <<- readRDS(cache_file)
  }
})

# Get profile for h-index and total citations
tryCatch({
  profile <- scholar::get_profile("aTyysxgAAAAJ")
}, error = function(e) {
  profile <- NULL
})
```

```{r}
#| output: asis
#| echo: false
#| warning: false
#| message: false

# Display profile statistics if available
if (!is.null(profile)) {
  cat("**Profile Statistics:**\n\n")
  cat("- **H-Index**: ", profile$h_index, "\n")
  cat("- **i10-Index**: ", profile$i10_index, "\n")
  cat("- **Total Citations**: ", profile$total_cites, "\n\n")
}

cat("### Peer-Reviewed Publications\n\n")

# Display publications from Google Scholar if available
if (!is.null(pubs) && nrow(pubs) > 0) {
  # Group by year
  years <- sort(unique(pubs$year), decreasing = TRUE)

  pub_counter <- 1
  total_pubs <- nrow(pubs)

  for (yr in years) {
    pubs_this_year <- pubs[pubs$year == yr, ]
    cat("#### ", yr, " (", nrow(pubs_this_year), " publication(s))\n\n")

    for (i in 1:nrow(pubs_this_year)) {
      pub <- pubs_this_year[i, ]

      # Format authors (bold Steven Hawken if present)
      authors <- bold_author(pub$author)

      # Build citation
      citation <- paste0(
        total_pubs - pub_counter + 1, ". ",
        authors, ". ",
        "**", pub$title, "**. ",
        "*", pub$journal, "*"
      )

      if (!is.na(pub$year) && pub$year != "") {
        citation <- paste0(citation, ", ", pub$year)
      }

      citation <- paste0(citation, ".")

      # Add citation count if available
      if (!is.na(pub$cites) && pub$cites > 0) {
        citation <- paste0(citation, " [", pub$cites, " citations]")
      }

      cat(citation, "\n\n")
      pub_counter <- pub_counter + 1
    }
  }
} else {
  cat("*Publications not currently available. Please check again later.*\n\n")
}
```

### Preprints

```{r}
#| output: asis
#| echo: false
#| warning: false
#| message: false

preprints <- cv_data$preprints

if (!is.null(preprints) && length(preprints) > 0) {
  for (preprint in preprints) {
    authors <- bold_author(preprint$authors)
    cat("**", preprint$title, "**\n\n")
    cat(authors, ". ")
    if (!is.null(preprint$date)) {
      cat(preprint$date, ". ")
    }
    cat(preprint$arxiv, "\n\n")
  }
} else {
  cat("*No preprints listed*\n\n")
}
```

---

```{r}
#| output: asis
#| echo: false
#| warning: false
#| message: false

# Footer with last updated date
update_date <- Sys.Date()
cat("**Last updated:** ", format(update_date, "%B %d, %Y"), "\n\n")
```
